Solar wind predictions for the Parker Solar Probe orbit

### 2017-11-08 paperMVVB/sections/content.tex
new folder referee_report_second

%\subsection{PSP solar wind environment estimation}
Implementing the SSN predictions for the PSP mission time and the orbital trajectory data, we can infer which solar wind parameter magnitudes can be expected. Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the median values (\ref{eq:median_with_ssn}) of the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the first closest perihelion in December 2024.
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}. For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_f_plot}
\end{figure}
% SSN sources and error ranges for first perihelion
% magnetic field:
% SWPC prediction - 0 years
% SWPC expected SSN ranges
% velocity:
% actual monthly SSN - 3 years
% not plotted
% density:
% actual monthly SSN - 6 years
% SIDC given std. dev. from stations
% temperature:
% actual monthly SSN - 3 years
% SIDC given std. dev. from stations
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2024 with PSP's 22nd (the first closest) perihelion at \SI{0.0459}{\au}. For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_nearest_f_plot}
\end{figure}
% SSN sources and error ranges for first closest perihelion
% magnetic field:
% actual monthly SSN - 11 years
% half/twice SSN
% velocity:
% actual monthly SSN - 14 years
% not plotted
% density:
% SWPC prediction - 0 years
% SWPC expected SSN ranges
% temperature:
% actual monthly SSN - 14 years
% half/twice SSN
In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the first closest approach at \SI{0.046}{\au}. \textbf{Monthly SSNs -- shifted by the time lags specific to the solar wind parameters -- are used in the calculation of the solar wind predictions. These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties. The error bands given in both figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.}
%B
% 87.3642361846083
%N
% 213.613795298952	first
% 2950.67837375615	nearest
% 2925.63248639046	SSN 0
% 3421.59065204775	SSN 200
%T
% 503136.759398494

>>>>

%\subsection{PSP solar wind environment estimation}
Implementing the SSN predictions for the PSP mission time and the orbital trajectory data, we can infer which solar wind parameter magnitudes can be expected. Figs.~\ref{fig:SPP_perihelia_prediction_f_plot} and \ref{fig:SPP_perihelia_prediction_nearest_f_plot} show the median values (\ref{eq:median_with_ssn}) of the considered different solar wind parameters for 12-day periods, comprising the first perihelion in Novemver 2018 and the first closest perihelion in December 2024.
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2018 with PSP's first perihelion at about \SI{0.16}{\au}. For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_f_plot}
\end{figure}
% SSN sources and error ranges for first perihelion
% magnetic field:
% SWPC prediction - 0 years
% SWPC expected SSN ranges
% velocity:
% actual monthly SSN - 3 years
% not plotted
% density:
% actual monthly SSN - 6 years
% SIDC given std. dev. from stations
% temperature:
% actual monthly SSN - 3 years
% SIDC given std. dev. from stations
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_nearest_f_plot.pdf}}
	\caption{Estimated solar wind parameter medians (black lines) and their error bands (grey) during 12~days in 2024 with PSP's 22nd (the first closest) perihelion at \SI{0.0459}{\au}. For the velocity the combined median is calculated and also the SSN-independent slow and fast parts are plotted (dotted lines).}
	\label{fig:SPP_perihelia_prediction_nearest_f_plot}
\end{figure}
% SSN sources and error ranges for first closest perihelion
% magnetic field:
% actual monthly SSN - 11 years
% half/twice SSN
% velocity:
% actual monthly SSN - 14 years
% not plotted
% density:
% SWPC prediction - 0 years
% SWPC expected SSN ranges
% temperature:
% actual monthly SSN - 14 years
% half/twice SSN
In the beginning of the mission median values of about \SI{87}{\nT}, \SI{340}{\km\per\s}, \SI{214}{\per\cm\cubed} and \SI{503000}{\K} are estimated to be measured at \SI{0.16}{\au}, increasing to about \SI{943}{\nT}, \SI{290}{\km\per\s}, \SI{2951}{\per\cm\cubed} and \SI{1930000}{\K} during the first closest approach at \SI{0.046}{\au}. Monthly SSNs -- shifted by the time lags specific to the solar wind parameters -- are used in the calculation of the solar wind predictions. These SSNs are either actual smoothed values from the SIDC with their reported standard deviations, short-term predictions from the SWPC with their expected ranges or actual smoothed values from the SIDC shifted by 11~years with half/twice their values as uncertainties. The error bands given in both figures, calculated from error propagation, include these SSN ranges and the derived fit parameter errors.
%B
% 87.3642361846083
%N
% 213.613795298952	first
% 2950.67837375615	nearest
% 2925.63248639046	SSN 0
% 3421.59065204775	SSN 200
%T
% 503136.759398494
